### 2013-10-31 descriptive_analysis.Rmd
Converting the code into RMarkdown and cleaning it..

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/code/")
library(kaRski)
knitpandoc("descriptive_analysis")

```{ropts, echo=FALSE}
opts_chunk$set(echo=FALSE, dev='svg', eval=TRUE, cache=TRUE, fig.height=10, message=FALSE, warning=FALSE)
```

<link href="http://markuskainu.fi/material/css/article_wide.css" rel="stylesheet" type="text/css" title="compact"></link>

@@

![Change in total GDP in 2007 - 2010 and support for social (left) and individual (right) blame types of attributions for poverty](../figure/scatter_gdp.png)

![Gini coefficient and support for social (left) and individual (right) blame types of attributions for poverty](../figure/scatter_gini.png)

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](../figure/scatter_wbgi.png)

>>>>

% Descriptive analysis

- [back to index](index.html)

`generated at:`
```{r, echo=FALSE}
Sys.time()
```
---

<link href="http://markuskainu.fi/material/css/rmarkdown.css" rel="stylesheet" type="text/css" title="compact"></link>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(kaRski)
knitpandoc("descriptive_analysis")
```

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

@@

![Change in total GDP in 2007 - 2010 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gdp.png)

![Gini coefficient and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gini.png)

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_wbgi.png)

### 2013-10-31 index.Rmd
Converting the code into RMarkdown and cleaning it..

@@

@@

@@

html-ouput                                                source code
-------------------------------------------------------   -----------------------------
[Descriptive analysis](code/descriptive_analysis.html)    [source](code/descriptive_analysis.Rmd)

@@

html-output                                               source code
-------------------------------------------------------   -----------------------------
[Article in html](article2013.html)                       [Article in pdf](article2013.pdf)

@@

html-ouput                                                source code
-------------------------------------------------------   -----------------------------
[Presentation slides](slides/slides_attrib.html)          [source](code/multilevel_models.Rmd)

>>>>

`generated at:`
```{r, echo=FALSE}
Sys.time()
```
---

@@

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

@@

This site gathers together all the data analysis behind the actual paper. Data analysis is broken down in three parts and each part is presented in .html format for human eyes and in text source including the R-code required for reproducing the analysis. As both the [micro data](http://www.ebrd.com/pages/research/publications/special/transitionII.shtml) and [macro data](http://www.qog.pol.gu.se/data/) are available as open data, anyone can rerun these analysis.

Analytical code is licensed under open [FreeBSD](http://en.wikipedia.org/wiki/BSD_licenses#2-clause_license_.28.22Simplified_BSD_License.22_or_.22FreeBSD_License.22.29)-licence.

@@

html-ouput                                                source code
-------------------------------------------------------   -----------------------------
[Descriptive analysis](descriptive_analysis.html)         [source](descriptive_analysis.Rmd)
[Graphics in the paper]()                                 [source](descriptive_analysis.Rmd)

@@

- [Article draft in .html](article2013.html)
- [Article draft in .pdf](article2013.pdf)
- [Article draft in .epub](article2013.epub)

@@

- HSE Moscow - November 12, 2013
- Jatkokoulutusseminaari Turku November 7, 2013
- [ESA Torino - August 29, 2013](torino2013/TorinoSlides2013_final.html)
